---
title: Running OncoScore
output: html_document
---

The OncoScore analysis consists of two parts. One can estimate a score to asses 
the oncogenic potential of a set of genes, given the lecterature knowledge, 
at the time of the analysis, or one can study the trend of such score over time.

We next present the two analysis and we conclude with showing the capabilities
of the tool to visualize the results. 

First we load the library.

```{r}
library("OncoScore")
```

The query that we show next retrieves from PubMed the citations, at the time of the 
query, for a list of genes in cancer related and in all the documents. 

```{r}
query = perform.query(c("ASXL1","IDH1","IDH2","SETBP1","TET2"))
```

OncoScore provides a function to merge gene names if requested by the user.
This function is useful when there are aliases in the gene list. 

```{r}
combine.query.results(query, c('IDH1', 'IDH2'), 'new_gene')
```

OncoScore also provides a function to retireve the names of the genes in a given 
portion of a chromosome that can be exploited if we are dealing, e.g., with copy 
number alterations hitting regions rather than specific genes. 

```{r eval=FALSE}
chr13 = get.genes.from.biomart(chromosome=13,start=54700000,end=72800000)
```

Furthermore, one can also automatically perform the OncoScore analysis on
chromosomic regions as follows: 

```{r eval=FALSE}
result = compute.oncoscore.from.region(10, 100000, 500000)
```

We now compute a score for each of the genes, to estimate their oncogenic
potential.

```{r}
result = compute.oncoscore(query)
```

The query that we show next retrieves from PubMed the citations, at specified time points, 
for a list of genes in cancer related and in all the documents.

```{r}
query.timepoints = perform.query.timeseries(c("ASXL1","IDH1","IDH2","SETBP1","TET2"),
    c("2012/03/01", "2013/03/01", "2014/03/01", "2015/03/01", "2016/03/01"))
```

We now compute a score for each of the genes, to estimate their oncogenic
potential at specified time points.

```{r}
result.timeseries = compute.oncoscore.timeseries(query.timepoints)
```

We next plot the scores measuring the oncogenetic potential of the considered genes as 
a barplot.

```{r fig.width=12, fig.height=8, warning=FALSE, fig.cap="Oncogenetic potential of the considered genes."}
plot.oncoscore(result, col = 'darkblue')
```

We finally plot the trend of the scores over the considered times as 
absolute and values and as variations.

```{r fig.width=12, fig.height=8, warning=FALSE, fig.cap="Absolute values of the oncogenetic potential of the considered genes over times."}
plot.oncoscore.timeseries(result.timeseries)
```

```{r fig.width=12, fig.height=8, warning=FALSE, fig.cap="Variations of the oncogenetic potential of the considered genes over times."}
plot.oncoscore.timeseries(result.timeseries, incremental = TRUE, ylab='absolute variation')
```

```{r fig.width=12, fig.height=8, warning=FALSE, fig.cap="Variations as relative values of the oncogenetic potential of the considered genes over times."}
plot.oncoscore.timeseries(result.timeseries, incremental = TRUE, relative = TRUE, ylab='relative variation')
```
