---
title: "Introduction"
author: 
  - Luca De Sano
  - Carlo Gambacorti Passerini
  - Rocco Piazza
  - Daniele Ramazzotti
  - Roberta Spinelli
date: "`r format(Sys.time(), '%B %d, %Y')`"
graphics: yes
package: OncoScore
output:
  BiocStyle::html_document:
    toc_float: true
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{OncoScore,BiocStyle}
---

## Overview

*OncoScore* is a tool to measure the association of genes to cancer based on citation 
frequency in biomedical literature. The score is evaluated from PubMed literature by 
dynamically updatable web queries. 

```{r include=FALSE}
library(knitr)
opts_chunk$set(
concordance = TRUE,
background = "#f3f3ff"
)
```

## Installing OncoScore

The R version of *OncoScore* can be installed from Github. To do so, we need to install the R packages *OncoScore* depends on and the devtools package. 


```{r eval=FALSE}
# install OncoScore dependencies
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("biomaRt")

# install OncoScore library
if (!require("devtools")) install.packages("devtools")
library("devtools")
install_github("danro9685/OncoScore", ref = "master")

# load OncoScore library
library("OncoScore")
```

## Debug

Please feel free to contact us if you have problems running our tool at daniele.ramazzotti1@gmail.com. 
